---
title: "POL40950: Introduction to Statistics"
subtitle: 'Lab Session: Week 7'
author: "Module Coordinator: [Stefan Müller](https://muellerstefan.net)"
date: "9 November 2020"
output: 
 html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Today, we will reproduce the main analysis in [Klüver and Spoon (2020)](https://www.journals.uchicago.edu/doi/pdf/10.1086/708239). **In order to reproduce the analysis, you must store the replication dataset (also on Brightspace in the Lab Sessions folder) in the same folder as this Rmd file.**

We will reproduce Table 1 of the paper.

Let's first import the dataset.

```{r, message=FALSE}
# load rio package to import dataset stored as .dta
library(rio)

dat_parties <- import("/Users/ypi/Desktop/replication_journal_of_politics.dta")
```


1. Model 1 of Table 1 only includes government parties. To ensure that we are working with the correct subset, please filter only government parties `filter(cabinet_party == 1)` and store the output in a new object called `dat_gov`. How many observations are included in this filtered dataset?

```{r, message=FALSE}
library(tidyverse)

dat_gov <- filter(dat_parties, cabinet_party == 1)

nrow(dat_gov)

# 460 observations are included, each observation is one cabinet party in one of the countries
```


2. Recode the variable `junior` in such a way that 1 is recoded as "Junior coalition party" and 0 as "Senior coalition party". (Solution below)

```{r}
table(dat_gov$junior)

# use dplyr's recode function
dat_gov <- dat_gov %>% 
    mutate(junior_senior = dplyr::recode(junior,
                                  "1" = "Junior coalition party",
                                  "0" = "Senior coalition party"))

table(dat_gov$junior_senior)
```

3. Testing the relationship between government status (junior or senior coalition party) and vote share at the next election: run a linear regression (`lm()`) with vote share at the next election (`next_pervote`) as the dependent variable, and the binary indicator of junior/senior coalition party (`junior`) as the independent variable.

```{r, message=FALSE}
lm_simple  <- lm(next_pervote ~ junior, data = dat_gov)

summary(lm_simple)
```

```{r, results='asis',messag=FALSE}
# use texreg package for nice regression table
library(texreg)

htmlreg(lm_simple)
```

3. Interpret the coefficient for `junior` in your group? Afterwards, discuss why a simple regression is not sufficient here. Which variables might be omitted and should be included?

_Moving from 0 (senior party) to 1 (junior coalition party) decreases the predicted vote share at the next election by around 17 percentage points. The intercept can be interpreted as follows: a senior coalition party (because 0 = senior) has an predicted vote share of 27 percent at the upcoming next election._

_Various alternative factors (apart from being a coalition party) influence vote share at elections. Klüver and Spoon discuss these control variables on pages 10-12. One example is previous vote share: if a party obtained 30 percent of the votes in election $t$ (the previous election) it is highly unlikely that the party only receives 3 percent in election $t+1$ (the next election). We need to control for such factors to get a credible estimate of the relationship between being a junior coalition party or the senior coalition party._

4. Reproduce Model 1 of Table 1 by including the following variables:

- Dependent variable: `next_pervote`
- Independent variables:  `junior`, `niche_party`, `seatshare`, `policy_extreme_logit`, `conflict_logit_new`, `pervote`

Do your coefficients correspond with the coefficients reported in the paper?

```{r}
lm_multiple <-  lm(next_pervote ~ junior +
                       niche_party +
                       seatshare + 
                       policy_extreme_logit+ 
                       conflict_logit_new + 
                       pervote, 
                   data = dat_gov)

summary(lm_multiple)
```

```{r, results='asis'}
# create a nice regression table
texreg::htmlreg(lm_multiple, digits = 3,
        custom.coef.names = c(
            "Intercept",
            "Junior coalition party (ref.: senior partner)",
            "Niche party",
            "Seat share",
            "Policy extremism",
            "Cabinet conflict",
            "Lagged dependent variable (previous vote share)"),
        caption = "The electoral performance of junior and senior coalition parties")
```

_Yes, the coefficient estimates are the same as the coefficients reported by Klüver and Spoon (2020). They use "Constant" instead of "Intercept", but it means the same._


5. BONUS: Interpret the coefficient of each variable. And why does the coefficient for `junior` change so drastically when comparing it to the model you ran in Question 3?

_For example: the estimate of −6.049 for junior coalition partners suggests that for any fixed values of all other independent variables, the average decrease in vote share for a junior coalition party (relative to a senior coalition party) amounts to 6.04 percentage points. Alternatively, we can state that the predicted vote share decreases by 6.04 percentage points when a party is a junior coalition party (as opposed to being the senior party), holding all other variables in the model constant._

_In the second model, we control for relevant variables which puts the coefficient for `junior` into perspective. $R^2$ also increases drastically, suggesting that the control variables improve model fit._

```{r}

library(tidyverse)
library(moderndive)
library(skimr)
library(ISLR)

evals_ch6 <- evals %>%
  select(ID, score, age, gender)


# glimpse will show the data structure  
glimpse(evals_ch6)

evals_ch6 %>% skim()


```

```{r}
evals_ch6 %>% get_correlation(formula=score~ age)


ggplot(evals_ch6,aes(x=age,y=score,color=gender))+
    geom_point()+geom_smooth(method='lm',se=F)
    labs(x = "Age", y = "Teaching Score", color = "Gender") 
    

# fits a different regression line for each group.


```

# Interaction model

```{r}

score_model_interaction<-lm(score~age*gender,data=evals_ch6)


get_regression_table(score_model_interaction)


```

#  Parallel slope model
## parallel slopes models still allow for different intercepts but force all lines to have the same slope. 

```{r}
ggplot(evals_ch6,aes(x=age,y=score,color=gender))+
    geom_point()+
    geom_parallel_slopes(se=F)+labs(x = "Age", y = "Teaching Score", color = "Gender")




```
